Towards practical probabilistic programming

### 2018-10-31 abstract/paper.tex
starting

# Towards practical probabilistic programming

We present our view on practical probabilistic programming, as
well as an inference facility for Go programs following the
view. Probabilistic programming promises to free the
practitioner from burden of re-implementing inference paradigms
and algorithms. There are dozens of probabilistic programming
languages currently in development. Yet, integrating
probabilistic programming inference into a software system
requires greater effort than writing a custom simulation and
inference algorithm. Probabilistic programming remains, at best,
a tool for modeling and prototyping.

We believe that the probabilistic programming approach can be
made practical. However, this requires a shift from design of
languages best suited for probabilistic inference to design
of tools and libraries which make probabilistic programming
in modern general-purpose languages accessible and convenient.

>>>>

\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

\acmConference[LAFI'2019]{Languages for Inference}{January 15,
2019}{Lisbon, Portugal}

\setcopyright{none}

\bibliographystyle{ACM-Reference-Format}

\begin{abstract}
We present a view on practical probabilistic programming, as
well as an inference facility for Go programs following the
view. Probabilistic programming promises to free the
practitioner from burden of re-implementing inference paradigms
and algorithms. There are dozens of probabilistic programming
languages currently in development. Yet, integrating
probabilistic programming inference into a software system
requires greater effort than writing a custom simulation and
inference algorithm. Probabilistic programming remains, at best,
a tool for modeling and prototyping.

We believe that the probabilistic programming approach can be
made practical. However, this requires a shift from design of
languages best suited for probabilistic inference to design of
tools and libraries which make probabilistic programming in
modern general-purpose languages accessible and convenient.
Here, we first discuss the challenges in practical use of
existing probabilistic programming systems, and then outline the
guidelines to implementation of a practical probabilistic
programming facility. We illustrate these guidelines on an
early-stage implementation of probabilistic programming facility
for the Go programming language. 
\end{abstract}

\begin{document}

\title{Towards practical probabilistic programming}
\author{David Tolpin}
\affiliation{
    \institution{PUB+}
    \country{Israel}
}
\email{david.tolpin@gmail.com}

\maketitle

\section{Challenges in Practice of Probabilistic Programming}

\section{Guidelines to a Practical Probabilistic Programming
Facility}

\section{Case Study: Probabilistic Programming Facility for
Go}

\bibliography{refs}

\end{document}
